QPLIB: A Library of Quadratic Programming Instances

### 2017-01-30 format.tex
fixup formatting of appendix tables

\vspace*{2mm}

%\vspace*{-10mm}
%{\tiny
%\LTcapwidth=16.17cm
\begin{longtable}{|llr|}

@@

%\begin{tabular}{|llr|}
%\hline

@@

$h$\; $k$\; $Q_{hk}^0$ & \lbox{row and column indices (integers) and value (real)
for each nonzero entry of $Q^0$, if $n^{Q^0} > 0$, one triple on each line} & \\

@@

$j$\; $b^0_j$ & \lbox{index (integer) and value (real) for each non-default
term in $b^0$, if $n^{b^0} > 0$, one pair per line} & \\

@@

& \lbox{constraint, row and column indices (integers) and value (real) for
 each entry of $Q^{i}$, if $n^{Q^i}$, one quadruple on each line} & \\

@@

$i$\; $j$\; $b^i_{j}$ & \lbox{row and column indices (integers) and value (real)

@@

entry of $b^i$, if $n^{b} > 0$, one triple on each line} & \\

@@

$c_{\infty}$ & \lbox{value (real) for infinity for constraint or variable

@@

is infinite} & \\

@@

$i$\;\ $c^i_{l}$ & \lbox{index (integer) and value (real) for each non-default

@@

in $c_{l,d}$, if $n^{c_{l,d}} > 0$, one pair per line}        & [2] \\

@@

$i$\;\ $c^i_{u}$ & \lbox{index (integer) and value (real) for each non-default

@@

in $c_{u,d}$, if $n^{c_{u,d}} > 0$, one pair per line}        & \\

@@

$i$\;\ $l_{i}$ & \lbox{index (integer) and value (real) for each non-default

@@

in $l$, if $n^{l_{d}}> 0$, one pair per line}        &  \\

@@

$i$\;\ $u_{i}$ & \lbox{index (integer) and value (real) for each non-default

@@

in $u$, if $n^{u_{d}}> 0$, one pair per line}        &  \\

@@

$v_d$ & \lbox{default variable type  (integer, 0 for continuous variables,
 1 for integer variables)} & [5] \\

@@

$i$\; $v_i$ & \lbox{index  and type (integers) for each non-default
variable type, if  $n^v > 0$, one pair per line} & [5] \\

@@

$x\s{0}_d$ & \lbox{default value (real) for the components of the starting
point  $x^0$ for the  variables $x$} & \\

@@

$i$\; $x_i^0$ & \lbox{index (integer) and value (real) for each non-default
starting value in $x^0$, if $n^{x^0} > 0$, one pair per line} &  \\

@@

$y\s{0}_d$ & \lbox{default value (real) for the components of the starting

@@

constraints} &  [2] \\

@@

$i$\; $y_i^0$ & \lbox{index (integer) and value (real) for each non-default
starting value in $y^0$, if $n^{y^0} > 0$, one pair per line} &  [2] \\

@@

$z\s{0}_d$ & \lbox{default value (real) for the components of the starting
point $z^0$ for the dual variables $z$ for the simple bound constraints} & \\

@@

$i$\; $z_i^0$ & \lbox{index (integer) and value (real) for each
non-default starting value in $z^0$, if $n^{z^0} > 0$, one pair per line} &  \\

@@

$n^x_d$ & \lbox{number of non-default names (integer) of variables---default

@@

value $i$} &  \\
$j$\; $\texttt{var\_name}_j$ & \lbox{index (integer) and name (character string)
for each non-default variable name, if $n^x_d > 0$,  one pair per line} & \\

@@

$n^c_d$ & \lbox{number of non-default names (integer) of general

@@

the numerical value $i$} &  \\
$i$\; $\texttt{cons\_name}_i$ & \lbox{index  (integer) and name (character string) for each
non-default constraint name, if $n^c_d > 0$,  one pair per line} & \\

@@

%}
%

%\end{tabular}

\renewcommand{\descriptionlabel}[1]{\hspace{\labelsep}\texttt{#1}}

\begin{description}
\item [{[1]}]
%\todo[inline]{\small Fabio and Emiliano: we think that, if possible, we should follow the classification proposed in Section 2.}

@@

{\small
\begin{verbatim}
! ---------------
! example problem
! ---------------
MIPBAND   # problem name
MIQP      # problem is a mixed-integer quadratic program
Minimize  # minimize the objective function
3         # variables
2         # general linear constraints
5         # nonzeros in lower triangle of Q^0
1 1 2.0   5 lines of row & column index & value of nonzeros in lower triangle Q^0
2 1 -1.0  |
2 2 2.0   |
3 2 -1.0  |
3 3 2.0   |
-0.2      default value for entries in b_0
1         # non default entries in b_0
2 -0.4    1 lines of index & value of non-default values in b_0
0.0       value of q^0
4         # nonzeros in vectors b^i (i =0,...,m)
1 1 1.0   4 lines of row & column index & value of nonzeros in b^i (i =0,...,m)
1 2 1.0   |
2 1 1.0   |
2 3 1.0   |
1.0E+20   infinity
1.0       default value for entries in c_l
0         # non default entries in c_l
1.0E+20   default value for entries in c_u
0         # non default entries in c_u
0.0       default value for entries in l
0         # non default entries in l
1.0       default value for entries in u
1         # non default entries in u
2 2.0     1 line of non-default indices and values in u
0         default variable type is continuous
1         # non default variable types
3 1       variable 3 is integer
1.0       default value for initial values for x
0         # non default entries in x
0.0       default value for initial values for y
0         # non default entries in y
0.0       default value for initial values for z
0         # non default entries in z
0         # non default names for variables
0         # non default names for constraints
\end{verbatim}
}

>>>>

\begin{longtable}{|lp{.7\textwidth}r|}

@@

@@

$h$\; $k$\; $Q_{hk}^0$ & row and column indices (integers) and value (real)
for each nonzero entry of $Q^0$, if $n^{Q^0} > 0$, one triple on each line & \\

@@

$j$\; $b^0_j$ & index (integer) and value (real) for each non-default
term in $b^0$, if $n^{b^0} > 0$, one pair per line & \\

@@

& constraint, row and column indices (integers) and value (real) for
 each entry of $Q^{i}$, if $n^{Q^i}$, one quadruple on each line & \\

@@

$i$\; $j$\; $b^i_{j}$ & row and column indices (integers) and value (real)

@@

entry of $b^i$, if $n^{b} > 0$, one triple on each line & \\

@@

$c_{\infty}$ & value (real) for infinity for constraint or variable

@@

is infinite & \\

@@

$i$\;\ $c^i_{l}$ & index (integer) and value (real) for each non-default

@@

in $c_{l,d}$, if $n^{c_{l,d}} > 0$, one pair per line        & [2] \\

@@

$i$\;\ $c^i_{u}$ & index (integer) and value (real) for each non-default

@@

in $c_{u,d}$, if $n^{c_{u,d}} > 0$, one pair per line        & \\

@@

$i$\;\ $l_{i}$ & index (integer) and value (real) for each non-default

@@

in $l$, if $n^{l_{d}}> 0$, one pair per line        &  \\

@@

$i$\;\ $u_{i}$ & index (integer) and value (real) for each non-default

@@

in $u$, if $n^{u_{d}}> 0$, one pair per line        &  \\

@@

$v_d$ & default variable type  (integer, 0 for continuous variables,
 1 for integer variables) & [5] \\

@@

$i$\; $v_i$ & index  and type (integers) for each non-default
variable type, if  $n^v > 0$, one pair per line & [5] \\

@@

$x\s{0}_d$ & default value (real) for the components of the starting
point  $x^0$ for the  variables $x$ & \\

@@

$i$\; $x_i^0$ & index (integer) and value (real) for each non-default
starting value in $x^0$, if $n^{x^0} > 0$, one pair per line &  \\

@@

$y\s{0}_d$ & default value (real) for the components of the starting

@@

constraints &  [2] \\

@@

$i$\; $y_i^0$ & index (integer) and value (real) for each non-default
starting value in $y^0$, if $n^{y^0} > 0$, one pair per line &  [2] \\

@@

$z\s{0}_d$ & default value (real) for the components of the starting
point $z^0$ for the dual variables $z$ for the simple bound constraints & \\

@@

$i$\; $z_i^0$ & index (integer) and value (real) for each
non-default starting value in $z^0$, if $n^{z^0} > 0$, one pair per line &  \\

@@

$n^x_d$ & number of non-default names (integer) of variables---default

@@

value $i$ &  \\
$j$\; $\texttt{var\_name}_j$ & index (integer) and name (character string)
for each non-default variable name, if $n^x_d > 0$,  one pair per line & \\

@@

$n^c_d$ & number of non-default names (integer) of general

@@

the numerical value $i$ &  \\
$i$\; $\texttt{cons\_name}_i$ & index  (integer) and name (character string) for each
non-default constraint name, if $n^c_d > 0$,  one pair per line & \\

@@

\renewcommand{\descriptionlabel}[1]{\hspace{\labelsep}\texttt{#1}}
\begin{description}
\item [{[1]}]
%\todo[inline]{\small Fabio and Emiliano: we think that, if possible, we should follow the classification proposed in Section 2.}

@@

{\small
\begin{verbatim}
! ---------------
! example problem
! ---------------
MIPBAND   # problem name
MIQP      # problem is a mixed-integer quadratic program
Minimize  # minimize the objective function
3         # variables
2         # general linear constraints
5         # nonzeros in lower triangle of Q^0
1 1 2.0   5 lines row & column index & value of nz. in lower triangle Q^0
2 1 -1.0  |
2 2 2.0   |
3 2 -1.0  |
3 3 2.0   |
-0.2      default value for entries in b_0
1         # non default entries in b_0
2 -0.4    1 lines of index & value of non-default values in b_0
0.0       value of q^0
4         # nonzeros in vectors b^i (i =0,...,m)
1 1 1.0   4 lines row & column index & value of nz. in b^i (i =0,...,m)
1 2 1.0   |
2 1 1.0   |
2 3 1.0   |
1.0E+20   infinity
1.0       default value for entries in c_l
0         # non default entries in c_l
1.0E+20   default value for entries in c_u
0         # non default entries in c_u
0.0       default value for entries in l
0         # non default entries in l
1.0       default value for entries in u
1         # non default entries in u
2 2.0     1 line of non-default indices and values in u
0         default variable type is continuous
1         # non default variable types
3 1       variable 3 is integer
1.0       default value for initial values for x
0         # non default entries in x
0.0       default value for initial values for y
0         # non default entries in y
0.0       default value for initial values for z
0         # non default entries in z
0         # non default names for variables
0         # non default names for constraints
\end{verbatim}
}
